Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-09 manuscript/manuscript.Rmd
start writing

# Predictive Modeling with GLM and a Minimalist Neural Network

In this section, we describe, fit, and evaluate both a GLM and a minimalist neural network architecture utilizing
embeddings. While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
reference since most actuaries are familiar with the technique. The working example for our experiments is as follows: 
Given a set of claims characteristics, we predict the losses paid on the property coverage of the policy. In the rest of 
this section, we describe the dataset we use, describe formally the models being considered, and discuss results.

## NFIP data

@@

```{r variables, results='asis', echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~Variable, ~Type,
  "Building insurance coverage", "Numeric",
  "Basement enclosure type", "Categorical",
  "Number of floors in the insured building", "Categorical (binned in original dataset)",
  "Flood zone", "Categorical (high cardinality)",
  "Primary residence", "Categorical (binary indicator)"
)
knitr::kable(
  variables,
  caption = "Predicator variables.",
  booktabs = TRUE,
  table.env = "table",
  escape = FALSE,
  linesep = ""
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

## Severity GLM

While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of establishing a
baseline model, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:

@@

## A Simple Neural Network

@@

# Interpretations {#interpretation}

@@

# Transfer Learning {#tl}

- get weights from NN and use in place of categorical variables in GLM?
- train GLM using backprop w/ embedding layer (OK maybe this ought to be absorbed in the modeling section and we add this as a separate model?)

>>>>

# Predictive Modeling with Embeddings

In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
procedure.

## Problem Description and Data

The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
on the property coverage of the policy.

@@

```{r variables, results='asis', message=FALSE, echo = FALSE}
library(magrittr)
variables <- tibble::tribble(
  ~Variable, ~Type,
  "Building insurance coverage", "Numeric",
  "Basement enclosure type", "Categorical",
  "Number of floors in the insured building", "Categorical (binned in original dataset)",
  "Flood zone", "Categorical (high cardinality)",
  "Primary residence", "Categorical (binary indicator)"
)
knitr::kable(
  variables,
  caption = "Predicator variables.",
  booktabs = TRUE,
  table.env = "table",
  escape = FALSE,
  linesep = ""
) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

## Models

1. A GLM with gamma distribution and log link function
2. A linear model with categorical embeddings and an exponential output activation
3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2.
4. A multilayer perceptron regression model

### Model 1: Simple GLM

While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
reference since most actuaries are familiar with the technique. 
While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of establishing a
baseline model, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:

@@

### Model 2: Linear Model with Embeddings

@@

## Interpretations {#interpretation}

@@
